Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-03-31 parts/sa.tex
update example

\begin{figure}[p]
  \centering
  \begin{tikzpicture}[aS,node distance=1.5cm]
    \node[Aproc] (c1) {$c_1$};
    \node[Aobj,below of=c1] (c01) {$\PHobj{c_0}{c_1}$};
    \node[Asol,below of=c01] (c01s) {};

    \node[Aproc,below of=c01s] (ab11) {$ab_{11}$};
    \node[Aobj,below right of=ab11] (ab0111) {$\PHobj{ab_{01}}{ab_{11}}$};
    \node[Asol,below of=ab0111] (ab0111s) {};
    \node[Aobj,below of=ab11,node distance=2.5cm] (ab0011) {$\PHobj{ab_{00}}{ab_{11}}$};
    \node[Asol,below of=ab0011] (ab0011s) {};
    \node[Aobj,below left of=ab11] (ab1011) {$\PHobj{ab_{10}}{ab_{11}}$};
    \node[Asol,below of=ab1011] (ab1011s) {};

    \node[Aproc,below of=ab0111s] (a1) {$a_1$};
    \node[Aobj,below of=a1] (a11) {$\PHobj{a_1}{a_1}$};
    \node[Asol,below of=a11] (a11s) {};
    \node[Aobj,below right of=a1] (a01) {$\PHobj{a_0}{a_1}$};
    \node[Asol,below of=a01] (a01s) {};
    \node[Aproc,below of=a01s] (b0) {$b_0$};
    \node[Aobj,below of=b0] (b00) {$\PHobj{b_0}{b_0}$};
    \node[Asol,below of=b00] (b00s) {};
    \node[Aobj,below right of=b0] (b10) {$\PHobj{b_1}{b_0}$};
    \node[Asol,below of=b10] (b10s) {};

    \node[Aproc,below of=ab1011s] (b1) {$b_1$};
    \node[Aobj,below of=b1] (b01) {$\PHobj{b_0}{b_1}$};
    \node[Asol,below of=b01] (b01s) {};
    \node[Aproc,below of=b01s] (a0) {$a_0$};
    \node[Aobj,below of=a0] (a10) {$\PHobj{a_1}{a_0}$};
    \node[Asol,below of=a10] (a10s) {};

    \path
    (c1) edge (c01)
    (c01) edge (c01s)
    (c01s) edge (ab11)
    (ab11) edge (ab0011) edge (ab0111) edge (ab1011)
    (ab0011) edge (ab0011s)
    (ab1011) edge (ab1011s)
    (ab0111) edge (ab0111s)

    (ab0011s) edge (a1) edge (b1)
    (ab1011s) edge (b1)
    (ab0111s) edge (a1)

    (a1) edge (a01) edge (a11)
    (a01) edge (a01s)
    (a01s) edge (b0)
    (a11) edge (a11s)
    (a0) edge (a10)
    (a10) edge (a10s)

    (b0) edge (b10) edge (b00)
    (b10) edge (b10s)
    (b00) edge (b00s)
    (b1) edge (b01)
    (b01) edge (b01s)
    (b01s) edge (a0)
    ;
    \path
    (ab0011) edge[double] (ab0111)
    (ab0011) edge[double,bend right=10] (ab1011)
    (ab1011) edge[double,bend right=10] (ab0011)
    (ab0111) edge[double,bend right=10] (ab1011)
    (ab1011) edge[double,bend right=10] (ab0111)
    ;
    \end{tikzpicture}
  \label{fig:sa-livelock}
  \caption{The local causality graph of the PH in \pref{fig:ph-livelock}.}
\end{figure}

>>>>

\begin{figure}[p]
  \centering
  \begin{tikzpicture}[aS]
    \node[Aproc] (c1) {$c_1$};
    \node[Aobj,below of=c1] (c01) {$\PHobj{c_0}{c_1}$};
    \node[Asol,below of=c01] (c01s) {};

    \node[Aproc,below of=c01s] (ab11) {$ab_{11}$};
    \node[AsolPrio,below of=ab11] (ab11s) {};

    \node[Aproc,below left of=ab11s] (a1) {$a_1$};
    \node[Aobj,below of=a1] (a11) {$\PHobj{a_1}{a_1}$};
    \node[Asol,below of=a11] (a11s) {};
    \node[Aobj,below left of=a1] (a01) {$\PHobj{a_0}{a_1}$};
    \node[Asol,below of=a01] (a01s) {};
    \node[Aproc,below of=a01s] (b0) {$b_0$};
    \node[Aobj,below of=b0] (b00) {$\PHobj{b_0}{b_0}$};
    \node[Asol,below of=b00] (b00s) {};
    \node[Aobj,below left of=b0] (b10) {$\PHobj{b_1}{b_0}$};
    \node[Asol,below of=b10] (b10s) {};

    \node[Aproc,below right of=ab11s] (b1) {$b_1$};
    \node[Aobj,below of=b1] (b11) {$\PHobj{b_1}{b_1}$};
    \node[Asol,below of=b11] (b11s) {};
    \node[Aobj,below right of=b1] (b01) {$\PHobj{b_0}{b_1}$};
    \node[Asol,below of=b01] (b01s) {};
    \node[Aproc,below of=b01s] (a0) {$a_0$};
    \node[Aobj,below of=a0] (a00) {$\PHobj{a_0}{a_0}$};
    \node[Asol,below of=a00] (a00s) {};
    \node[Aobj,below right of=a0] (a10) {$\PHobj{a_1}{a_0}$};
    \node[Asol,below of=a10] (a10s) {};

    \path
    (c1) edge (c01)
    (c01) edge (c01s)
    (c01s) edge (ab11)
    (ab11) edge (ab11s)
    (ab11s) edge (a1) edge (b1)

    (a1) edge (a01) edge (a11)
    (a01) edge (a01s)
    (a01s) edge (b0)
    (a11) edge (a11s)
    (a0) edge (a10) edge (a00)
    (a10) edge (a10s)
    (a00) edge (a00s)

    (b0) edge (b10) edge (b00)
    (b10) edge (b10s)
    (b00) edge (b00s)
    (b1) edge (b01) edge (b11)
    (b01) edge (b01s)
    (b01s) edge (a0)
    (b11) edge (b11s)
    ;
    \end{tikzpicture}
  \label{fig:sa-livelock}
  \caption{
    The graph of local causality of the PH model in \pref{fig:ph-livelock}.
    \pref{th:approxinf} is inconclusive on this example as the only solution of process $ab_{11}$ is not coherent (\pref{def:coherent}).
  }
\end{figure}
